Carrier phase and amplitude estimation of $M$-ary phase shift keying using pilots and data

### 2012-08-01 paper.tex
Added new data.  Looks like I have all the results now.  Just need to start filling in all the Lemmas!

\begin{lemma}\label{lem:k2conv}
$k_2(\hat{\lambda}_L) = \hat{\lambda}_L ( H + o_P(1) ).$
\end{lemma}
\begin{IEEEproof}
As $\hat{\lambda}_L \in [-\pi, \pi)$ it is only the behaviour of the function $k_2(\lambda)$ for $\lambda\in [-\pi, \pi)$ that is relevant.  We will analyse $k_2(\lambda)$ for $0 \leq \lambda < \tfrac{\pi}{M}$.  An analagous argument follows when $-\tfrac{\pi}{M} \leq \lambda < 0$.  To keep our notation clean put
\[
\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}.
\]
For each integer $k$, if $\Phi_1 \in [\psi_{k-1}, \psi_k)$, then
\[
\fracpart{\Phi_1} = \Phi_1 - \round{\Phi_1} = \Phi_1 - \tfrac{2\pi}{M}k.
\]
Similarly, if $\Phi_1 \in  [\psi_{k-1}, \psi_{k} - \lambda)$, then
\[
\fracpart{\Phi_1 + \lambda} = \Phi_1 + \lambda - \tfrac{2\pi}{M}k,
\]
whilst, if $\Phi_1 \in [\psi_{k} - \lambda, \psi_{k})$, then
\[
\fracpart{\Phi_1 + \lambda} = \Phi_1 + \lambda - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}.
\]
So, when $\Phi_1 \in [\psi_{k-1}, \psi_{k} - \lambda )$,
\begin{align*}
\sin\fracpart{\lambda + \Phi_1} - &\sin\fracpart{\Phi_1} \\
&= \sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k) - \sin(\Phi_1 - \tfrac{2\pi}{M}k),
\end{align*}
and by a Taylor expansion of $\sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k)$ about $\Phi_1 - \tfrac{2\pi}{M}k$, 
\begin{align*}
\sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} &= \lambda\big(\cos(\Phi_1 - \tfrac{2\pi}{M}k) + \zeta_k(\lambda)\big) \\
&= \lambda\big(\cos\fracpart{\Phi_1} + \zeta_k(\lambda)\big).
\end{align*}
where, for each integer $k$, the function $\zeta_k$ is continuous with $\zeta_k(0) = 0$.  Alternatively, when $\Phi_1 \in [ \psi_{k} - \lambda,\psi_{k})$,
\begin{align*}
\sin\fracpart{\lambda + \Phi_1} &- \sin\fracpart{\Phi_1} \\
&= \sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) - \sin(\Phi_1 - \tfrac{2\pi}{M}k)
\end{align*}
and by a Taylor expansion of $\sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M})$ about $\Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}$,
\begin{align*}
\sin&\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \\
&= s_k(\Phi_1) + \lambda\big(\cos(\Phi_1 - \tfrac{2\pi k}{M}) + c_k(\Phi_1) + \zeta_{k+1}(\lambda)\big)
\end{align*}
where
\[
s_k(\Phi_1) = \sin(\Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) - \sin(\Phi_1 - \tfrac{2\pi}{M}k),
\]
and
\[
c_k(\Phi_1) = \cos(\Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) - \cos(\Phi_1 - \tfrac{2\pi k}{M}).
\]
Now,
\begin{align*}
\sin\fracpart{\lambda + \Phi_1} - &\sin\fracpart{\Phi_1}\\ 
&= s_k(\Phi_1) + \lambda\big(\cos\fracpart{\Phi_1} + \eta_k(\lambda, \Phi_1) \big),
\end{align*}
where $\eta_k(\lambda, \Phi_1) = c_k(\Phi_1) + \zeta_{k+1}(\lambda)$.  Both $s_k$ and $c_k$ are continuous functions and $s_k(\psi_{k}) = -2\sin(\tfrac{\pi}{M})$ and $c_k(\psi_{k}) = 0$.

Let us now collate what we have.  For each integer $k$, if $\Phi_1 \in [\psi_{k-1}, \psi_{k} - \lambda )$, then
\[
\sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} = \lambda\cos\fracpart{\Phi_1} + \lambda\zeta_k(\lambda),
\]
whilst, if $\Phi_1 \in [ \psi_{k} - \lambda,\psi_{k})$, then
\[
\sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} = \lambda \cos\fracpart{\Phi_1} + s_k(\Phi_1) + \lambda\eta_k(\lambda, \Phi_1).
\]
Since the intervals $[\psi_{k-1}, \psi_{k})$ partion the real line, that is $\reals = \cup_{k\in\ints}[\psi_{k-1}, \psi_{k})$, then, for all $\Phi_1 \in \reals$,
\[
\sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} = \lambda\cos\fracpart{\Phi_1} +  v(\lambda, \Phi_1) 
\]
where $v(\lambda, \Phi_1) = \sum_{k\in\ints} v_k(\lambda, \Phi_1)$ and
\begin{equation}\label{eq:vk}
v_k(\lambda,\Phi_1) = \begin{cases}
s_k(\Phi_1) + \lambda\eta_k(\lambda, \Phi_1) &  \Phi_1 \in [ \psi_{k} - \lambda,\psi_{k} ) \\
\lambda\zeta_k(\lambda) & \Phi_1 \in [\psi_{k-1}, \psi_{k} - \lambda ) \\
0 & \text{otherwise}.
\end{cases}
\end{equation}
Now we can write,
\begin{align*}
k_2(\lambda) &=  \expect R_1\big( \sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \big) \\
&= \expect R_1\big( \lambda\cos\fracpart{\Phi_1} + v(\lambda, \Phi_1)  \big) \\
&= \lambda h_2(0) + \expect R_1 v(\lambda, \Phi_1).
\end{align*}
Let $W(\lambda) = \expect R_1 v(\lambda, \Phi_1)$ so that $k_2(\lambda) = \lambda h_2(0) + W(\lambda).$  Lemma~\ref{lem:expRvlamphi} shows that $W(\lambda) =  \lambda(H_1 + \gamma(\lambda))$ where $\gamma(\lambda)$ is a function that goes to zero as $\lambda$ goes to zero, and
\[
H_1 = - 2 \sin(\tfrac{\pi}{M}) \sum_{k = 0}^{M-1} g(\psi_k) = H - h_2(0).
\]
Because $\hat{\lambda}_L$ converges almost surely to zero as $L \rightarrow\infty$, it follows that $\gamma(\hat{\lambda}_L) = o_P(1)$, and so
\[
k_2(\hat{\lambda}_L) = \hat{\lambda}_L ( h_2(0) + H_1 + o_P(1) ) = \hat{\lambda}_L ( H + o_P(1) )
\]
as required.  It remains to prove Lemma~\ref{lem:expRvlamphi}.
\end{IEEEproof}

\begin{lemma}\label{lem:expRvlamphi}
$W(\lambda) =  \lambda(H_1 + \gamma(\lambda))$ where $\gamma$ is a continuous function with $\gamma(0) = 0$.
\end{lemma}
\begin{IEEEproof}
In this lemma, as in Lemma~\ref{lem:k2conv}, we work under the assumption that $0 \leq \lambda < \frac{\pi}{M}$.  An analgous argument follows when $-\tfrac{\pi}{M} \leq \lambda < 0$.  Recalling that $f(r,\phi)$ is the joint probability density function of $R_1$ and $\Phi_1$, 
\begin{align}
W(\lambda) &= \expect R_1 v(\lambda, \Phi_1) \nonumber  \\
&= \int_0^{2\pi}\int_{0}^\infty r v(\lambda, \phi) f(r,\phi) dr d\phi \nonumber  \\ 
&= \int_0^{2\pi} v(\lambda, \phi) g(\phi) d\phi \nonumber \\
&= \sum_{k \in \ints} \int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi. \label{eq:Winfsum}
\end{align}
Now, when $0 < k < M$, we have $0 < \psi_{k-1} < \psi_k < 2\pi$, so, using~\eqref{eq:vk},
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) &g(\phi) d\phi = \int_{\psi_{k-1}}^{\psi_{k}} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \lambda a_k(\lambda) + \lambda b_k(\lambda) + \lambda d_k(\lambda),
\end{align*}
where, for $k = 1, \dots, M-1$,
\begin{equation}\label{eq:ak}
a_k(\lambda) = \int_{\psi_k-\lambda}^{\psi_k}\eta_k(\lambda, \phi) g(\phi) d\phi,
\end{equation}
\[
b_k(\lambda) = \zeta_k(\lambda) \int_{\psi_{k-1}}^{\psi_k -\lambda}g(\phi) d\phi,
\]
\begin{equation}\label{eq:ck}
d_k(\lambda) = \frac{1}{\lambda} \int_{\psi_{k} - \lambda}^{\psi_{k}} s_k(\phi) g(\phi) d\phi.
\end{equation}
Both $a_k(\lambda)$ and $b_k(\lambda)$ converge to zero as $\lambda$ goes to zero, and, since $g$ is continuous, $d_k(\lambda)$ converges to 
\[
s_k(\psi_k)g(\psi_k) = -2\sin(\tfrac{\pi}{M}) g(\tfrac{2\pi}{M}k + \tfrac{\pi}{M}).
\]
as $\lambda$ goes to zero from above\footnote{We actually only require $g$ to be continuous at $\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}$ for each $k = 0, 1, \dots, M-1$, and the requirements of Theorem~\ref{thm:normality} could be weakened in this sense.  Here, the continuity of $g$ is garaunteed by the assumption that the noise $w_1$ is circularly symetric.}.  We are only interested in the limits from above because we are working under the assumption that that $0 \leq \lambda < \frac{\pi}{M}$.  The analgous argument when $-\tfrac{\pi}{M} \leq \lambda < 0$ would involve limits as $\lambda$ approaches zero from below.

Now, when $k = 0$, we have $\psi_{-1} < 0 < \psi_0 - \lambda < \psi_0 < 2\pi$, so that
\[
\int_0^{2\pi} v_0(\lambda, \phi) g(\phi) d\phi = \lambda a_0(\lambda) + \lambda b_0(\lambda) +  \lambda c_0(\lambda),
\]
where $a_0(\lambda)$ and $c_0(\lambda)$ are defined as in~\eqref{eq:ak}~and~\eqref{eq:ck}, and
\[
b_0(\lambda) = \zeta_0(\lambda) \int_{0}^{\psi_k-\lambda} g(\phi) d\phi.
\]
When $k = M$, we have $0 < \psi_{M-1} < 2\pi < \psi_{M} - \lambda$, so that
\[
\int_0^{2\pi} v_{M}(\lambda, \phi) g(\phi) d\phi = \lambda b_{M}(\lambda)
\]
where 
\[
b_{M}(\lambda) = \zeta_{M}(\lambda) \int_{\psi_{M-1}}^{2\pi}g(\phi) d\phi.
\]
Both $b_0(\lambda)$ and $b_M(\lambda)$ are functions that converge to zero as $\lambda$ approaches zero from above.

Finally, when $k < 0$ or $k > M$, 
\[
\int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi = 0.
\]
So the infinite sum in~\eqref{eq:Winfsum} can be written as the finite sum,
\begin{align*}
W(\lambda) &= \sum_{k=0}^{M} \int_{0}^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \sum_{k=0}^{M-1} \lambda d_k(\lambda) + \sum_{k=0}^{M-1} \lambda a_k(\lambda) + \sum_{k=0}^{M} \lambda b_k(\lambda) \\
&= \lambda \left( D(\lambda)  + A(\lambda) + B(\lambda) \right),
\end{align*}
where 
\[
A(\lambda) = \sum_{k=0}^{M-1} a_k(\lambda), \;\;\; B(\lambda) = \sum_{k=0}^{M} b_k(\lambda), \;\;\; \text{and},
\]
\[
D(\lambda) = \sum_{k=0}^{M-1} d_k(\lambda).
\]
Both $A(\lambda)$ and $B(\lambda)$ converge to zero as $\lambda$ goes to zero, whilst $D(\lambda)$ converges to $H_1$ as $\lambda$ converges to zero.  Put
\[
\gamma(\lambda) = A(\lambda) + B(\lambda) + D(\lambda) - H_1.
\]
Then $\gamma(\lambda)$ converges to zero as $\lambda$ goes to zero and $W(\lambda) = \lambda(H_1 + \gamma(\lambda))$ as required.
\end{IEEEproof}

@@

\begin{lemma}\label{lem:convdistGLdash}
The distribution of $\sqrt{L}G_L'(0)$ converges to the normal with zero mean and variance $A_1 + A_2$.
\end{lemma}
\begin{IEEEproof}
Observe that 
\[
\sqrt{L} G_L^\prime(0) = \frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\Phi_i) + \frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin\sfracpart{\Phi_i}.
\]
From the standard central limit the distribution of
\[
\frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\Phi_i) = \sqrt{\frac{\abs{P}}{L}} \frac{1}{\sqrt{\abs{P}}} \sum_{i \in P} R_i \sin(\Phi_i) 
\]
converges to the normal with mean $k_1(0) = 0$ and variance 
\[
A_1 = p \expect R_1^2 \sin^2(\Phi_1).
\]
Similarly, the distribution of 
\[
\frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin\fracpart{\Phi_i} = \sqrt{\frac{\abs{D}}{L}} \frac{1}{\sqrt{\abs{D}}} \sum_{i \in D} R_i \sin\fracpart{\Phi_i} 
\]
converges to the normal with mean $k_2(0) = 0$ and variance
\[
A_2 = d \expect R_1^2 \sin^2\fracpart{\Phi_1}.
\]
\end{IEEEproof}

\begin{lemma}\label{lem:empiricprocforrho} BLERG
\[
\sqrt{L}\big( G_L(\hat{\lambda}_L) - H_L(\hat{\lambda}_L) \big) = o_P(1) + \sqrt{L} \big( G_L^\prime(0) - H_L(0) \big).
\]
\end{lemma}
\begin{IEEEproof}
\end{IEEEproof}

\begin{lemma}\label{lem:HLtoG} BLERG
\[
\sqrt{L}\big( H_L(\hat{\lambda}_L) - G(0) \big) = \hat{\lambda}_L \big( ? + o_P(1) \big).
\]
\end{lemma}
\begin{IEEEproof}
\end{IEEEproof}

\begin{lemma}\label{lem:XL} 
The distribution of $X_L$ converges to the normal with zero mean and covariance
\[
?
\]
as $L \rightarrow\infty$.
\end{lemma}
\begin{IEEEproof}

\begin{lemma}\label{lem:XLcovlambdaL} 
The covariance between $X_L$ and $\sqrt{L}\hat{\lambda}_L$ converges to zero as $L\rightarrow\infty$.
\end{lemma}
\begin{IEEEproof}

>>>>

\begin{lemma}\label{lem:k2conv}
$k_2(\hat{\lambda}_L) = \hat{\lambda}_L ( H + o_P(1) ).$
\end{lemma}
\begin{IEEEproof}
As $\hat{\lambda}_L \in [-\pi, \pi)$ it is only the behaviour of the function $k_2(\lambda)$ for $\lambda\in [-\pi, \pi)$ that is relevant.  We will analyse $k_2(\lambda)$ for $0 \leq \lambda < \tfrac{\pi}{M}$.  An analagous argument follows when $-\tfrac{\pi}{M} \leq \lambda < 0$.  To keep our notation clean put
\[
\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}.
\]
For each integer $k$, if $\Phi_1 \in [\psi_{k-1}, \psi_k)$, then
\[
\fracpart{\Phi_1} = \Phi_1 - \round{\Phi_1} = \Phi_1 - \tfrac{2\pi}{M}k.
\]
Similarly, if $\Phi_1 \in  [\psi_{k-1}, \psi_{k} - \lambda)$, then
\[
\fracpart{\Phi_1 + \lambda} = \Phi_1 + \lambda - \tfrac{2\pi}{M}k,
\]
whilst, if $\Phi_1 \in [\psi_{k} - \lambda, \psi_{k})$, then
\[
\fracpart{\Phi_1 + \lambda} = \Phi_1 + \lambda - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}.
\]
So, when $\Phi_1 \in [\psi_{k-1}, \psi_{k} - \lambda )$,
\begin{align*}
\sin\fracpart{\lambda + \Phi_1} - &\sin\fracpart{\Phi_1} \\
&= \sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k) - \sin(\Phi_1 - \tfrac{2\pi}{M}k),
\end{align*}
and by a Taylor expansion of $\sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k)$ about $\lambda = 0$, 
\begin{align*}
\sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} &= \lambda\big(\cos(\Phi_1 - \tfrac{2\pi}{M}k) + \zeta_k(\lambda)\big) \\
&= \lambda\big(\cos\fracpart{\Phi_1} + \zeta_k(\lambda)\big).
\end{align*}
where, for each integer $k$, the function $\zeta_k$ is continuous with $\zeta_k(0) = 0$.  Alternatively, when $\Phi_1 \in [ \psi_{k} - \lambda,\psi_{k})$,
\begin{align*}
\sin\fracpart{\lambda + \Phi_1} &- \sin\fracpart{\Phi_1} \\
&= \sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) - \sin(\Phi_1 - \tfrac{2\pi}{M}k)
\end{align*}
and by a Taylor expansion of $\sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M})$ about $\lambda = 0$,
\begin{align*}
\sin&\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \\
&= s_k(\Phi_1) + \lambda\big(\cos\fracpart{\Phi_1} + \eta_k(\lambda, \Phi_1)  )\big)
\end{align*}
where
\[
s_k(\Phi_1) = \sin(\Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) - \sin(\Phi_1 - \tfrac{2\pi}{M}k),
\]
and
\[
\eta_k(\lambda, \Phi_1) = \cos(\Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) - \cos(\Phi_1 - \tfrac{2\pi k}{M}) + \zeta_{k+1}(\lambda).
\]
Observe that $s_k$ is continuous and $s_k(\psi_{k}) = -2\sin(\tfrac{\pi}{M})$.

Let us now collate what we have.  For each integer $k$, if $\Phi_1 \in [\psi_{k-1}, \psi_{k} - \lambda )$, then
\[
\sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} = \lambda\cos\fracpart{\Phi_1} + \lambda\zeta_k(\lambda),
\]
whilst, if $\Phi_1 \in [ \psi_{k} - \lambda,\psi_{k})$, then
\[
\sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} = \lambda \cos\fracpart{\Phi_1} + s_k(\Phi_1) + \lambda\eta_k(\lambda, \Phi_1).
\]
Since the intervals $[\psi_{k-1}, \psi_{k})$ partion the real line, that is $\reals = \cup_{k\in\ints}[\psi_{k-1}, \psi_{k})$, it follows that for all $\Phi_1 \in \reals$,
\[
\sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} = \lambda\cos\fracpart{\Phi_1} +  v(\lambda, \Phi_1),
\]
where $v(\lambda, \Phi_1) = \sum_{k\in\ints} v_k(\lambda, \Phi_1)$ and
\begin{equation}\label{eq:vk}
v_k(\lambda,\Phi_1) = \begin{cases}
s_k(\Phi_1) + \lambda\eta_k(\lambda, \Phi_1) &  \Phi_1 \in [ \psi_{k} - \lambda,\psi_{k} ) \\
\lambda\zeta_k(\lambda) & \Phi_1 \in [\psi_{k-1}, \psi_{k} - \lambda ) \\
0 & \text{otherwise}.
\end{cases}
\end{equation}
Now,
\begin{align*}
k_2(\lambda) &=  \expect R_1\big( \sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \big) \\
&= \expect R_1\big( \lambda\cos\fracpart{\Phi_1} + v(\lambda, \Phi_1)  \big) \\
&= \lambda h_2(0) + \expect R_1 v(\lambda, \Phi_1).
\end{align*}
Let $W(\lambda) = \expect R_1 v(\lambda, \Phi_1)$ so that $k_2(\lambda) = \lambda h_2(0) + W(\lambda).$  Lemma~\ref{lem:expRvlamphi} shows that $W(\lambda) =  \lambda(H_1 + \gamma(\lambda))$ where $\gamma(\lambda)$ is a continuous function with $\gamma(0) = 0$, and
\[
H_1 = - 2 \sin(\tfrac{\pi}{M}) \sum_{k = 0}^{M-1} g(\psi_k) = H - h_2(0),
\]
where $H$ is defined in the statement of Theorem~\ref{thm:normality}.  Because $\hat{\lambda}_L$ converges almost surely to zero as $L \rightarrow\infty$, it follows that $\gamma(\hat{\lambda}_L) = o_P(1)$, and so
\[
k_2(\hat{\lambda}_L) = \hat{\lambda}_L ( h_2(0) + H_1 + o_P(1) ) = \hat{\lambda}_L ( H + o_P(1) )
\]
as required.  It remains to prove Lemma~\ref{lem:expRvlamphi}.
\end{IEEEproof}

\begin{lemma}\label{lem:expRvlamphi}
$W(\lambda) =  \lambda(H_1 + \gamma(\lambda))$ where $\gamma$ is a continuous function with $\gamma(0) = 0$.
\end{lemma}
\begin{IEEEproof}
In this lemma, as in Lemma~\ref{lem:k2conv}, we work under the assumption that $0 \leq \lambda < \frac{\pi}{M}$.  An analgous argument follows when $-\tfrac{\pi}{M} \leq \lambda < 0$.  Recalling that $f(r,\phi)$ is the joint pdf of $R_1$ and $\Phi_1$, 
\begin{align}
W(\lambda) &= \expect R_1 v(\lambda, \Phi_1) \nonumber  \\
&= \int_0^{2\pi}\int_{0}^\infty r v(\lambda, \phi) f(r,\phi) dr d\phi \nonumber  \\ 
&= \int_0^{2\pi} v(\lambda, \phi) g(\phi) d\phi \nonumber \\
&= \sum_{k \in \ints} \int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi. \label{eq:Winfsum}
\end{align}
Now, when $0 < k < M$, we have $0 < \psi_{k-1} < \psi_k < 2\pi$, so, using~\eqref{eq:vk},
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) &g(\phi) d\phi = \int_{\psi_{k-1}}^{\psi_{k}} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \lambda a_k(\lambda) + \lambda b_k(\lambda) + \lambda c_k(\lambda),
\end{align*}
where, for $k = 1, \dots, M-1$,
\begin{equation}\label{eq:ak}
a_k(\lambda) = \int_{\psi_k-\lambda}^{\psi_k}\eta_k(\lambda, \phi) g(\phi) d\phi,
\end{equation}
\[
b_k(\lambda) = \zeta_k(\lambda) \int_{\psi_{k-1}}^{\psi_k -\lambda}g(\phi) d\phi,
\]
\begin{equation}\label{eq:ck}
c_k(\lambda) = \frac{1}{\lambda} \int_{\psi_{k} - \lambda}^{\psi_{k}} s_k(\phi) g(\phi) d\phi.
\end{equation}
Both $a_k(\lambda)$ and $b_k(\lambda)$ converge to zero as $\lambda$ goes to zero, and, since $g$ is continuous, $c_k(\lambda)$ converges to 
\[
s_k(\psi_k)g(\psi_k) = -2\sin(\tfrac{\pi}{M}) g(\tfrac{2\pi}{M}k + \tfrac{\pi}{M})
\]
as $\lambda$ goes to zero from above\footnote{We actually only require $g$ to be continuous at $\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}$ for each $k = 0, 1, \dots, M-1$, and the requirements of Theorem~\ref{thm:normality} could be weakened in this sense.  Here, the continuity of $g$ is garaunteed by the assumption that the noise $w_1$ is circularly symetric.}.  We are only interested in the limit from above because we are working under the assumption that that $0 \leq \lambda < \frac{\pi}{M}$.  The analgous argument when $-\tfrac{\pi}{M} \leq \lambda < 0$ would involve limits as $\lambda$ approaches zero from below.

Now, when $k = 0$, we have $\psi_{-1} < 0 < \psi_0 - \lambda < \psi_0 < 2\pi$, so that
\[
\int_0^{2\pi} v_0(\lambda, \phi) g(\phi) d\phi = \lambda a_0(\lambda) + \lambda b_0(\lambda) +  \lambda c_0(\lambda),
\]
where $a_0(\lambda)$ and $c_0(\lambda)$ are defined as in~\eqref{eq:ak}~and~\eqref{eq:ck}, and
\[
b_0(\lambda) = \zeta_0(\lambda) \int_{0}^{\psi_k-\lambda} g(\phi) d\phi.
\]
When $k = M$, we have $0 < \psi_{M-1} < 2\pi < \psi_{M} - \lambda$, so that
\[
\int_0^{2\pi} v_{M}(\lambda, \phi) g(\phi) d\phi = \lambda b_{M}(\lambda)
\]
where 
\[
b_{M}(\lambda) = \zeta_{M}(\lambda) \int_{\psi_{M-1}}^{2\pi}g(\phi) d\phi.
\]
Both $b_0(\lambda)$ and $b_M(\lambda)$ are functions that converge to zero as $\lambda$ converges to zero.

Finally, when $k < 0$ or $k > M$, 
\[
\int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi = 0.
\]
So the infinite sum in~\eqref{eq:Winfsum} can be written as the finite sum,
\begin{align*}
W(\lambda) &= \sum_{k=0}^{M} \int_{0}^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \sum_{k=0}^{M-1} \lambda c_k(\lambda) + \sum_{k=0}^{M-1} \lambda a_k(\lambda) + \sum_{k=0}^{M} \lambda b_k(\lambda) \\
&= \lambda \left( C(\lambda)  + A(\lambda) + B(\lambda) \right),
\end{align*}
where 
\[
A(\lambda) = \sum_{k=0}^{M-1} a_k(\lambda), \;\;\; B(\lambda) = \sum_{k=0}^{M} b_k(\lambda), \;\;\; \text{and},
\]
\[
C(\lambda) = \sum_{k=0}^{M-1} c_k(\lambda).
\]
Both $A(\lambda)$ and $B(\lambda)$ converge to zero as $\lambda$ goes to zero, whilst $C(\lambda)$ converges to $H_1$ as $\lambda$ converges to zero.  Put
\[
\gamma(\lambda) = A(\lambda) + B(\lambda) + D(\lambda) - H_1.
\]
Then $\gamma(\lambda)$ converges to zero as $\lambda$ goes to zero and $W(\lambda) = \lambda(H_1 + \gamma(\lambda))$ as required.
\end{IEEEproof}

@@

\begin{lemma}\label{lem:convdistGLdash}
The distribution of $\sqrt{L}G_L'(0)$ converges to the normal with zero mean and variance $pA_1 + dA_2$.
\end{lemma}
\begin{IEEEproof}
Observe that 
\[
\sqrt{L} G_L^\prime(0) = \frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\Phi_i) + \frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin\sfracpart{\Phi_i}.
\]
From the standard central limit the distribution of
\[
\frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\Phi_i) = \sqrt{\frac{\abs{P}}{L}} \frac{1}{\sqrt{\abs{P}}} \sum_{i \in P} R_i \sin(\Phi_i) 
\]
converges to the normal with mean $\sqrt{p} k_1(0) = 0$ and variance
\[
p A_1 = p \expect R_1^2 \sin^2(\Phi_1).
\]
Similarly, the distribution of 
\[
\frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin\fracpart{\Phi_i} = \sqrt{\frac{\abs{D}}{L}} \frac{1}{\sqrt{\abs{D}}} \sum_{i \in D} R_i \sin\fracpart{\Phi_i} 
\]
converges to the normal with mean $\sqrt{d} k_2(0) = 0$ and variance
\[
d A_2 = d \expect R_1^2 \sin^2\fracpart{\Phi_1}.
\]
\end{IEEEproof}

\begin{lemma}\label{lem:empiricprocforrho} BLERG
\[
\sqrt{L}\big( G_L(\hat{\lambda}_L) - T(\hat{\lambda}_L) \big) = o_P(1) + X_L,
\]
where $X_L = \sqrt{L} \big( G_L(0) - T(0) \big)$.
\end{lemma}
\begin{IEEEproof}
The is the empirical process proof!
\end{IEEEproof}

\begin{lemma}\label{lem:HLtoG} BLERG
\[
\sqrt{L}\big( T(\hat{\lambda}_L) - G(0) \big) = o_P(1).
\]
\end{lemma}
\begin{IEEEproof}
The argument is similar to that used in Lemma~\ref{lem:Qconv}.  First observe that
\begin{align*}
T(\lambda) &= \frac{\abs{P}}{L}\expect R_1\cos(\lambda + \Phi_1) + \frac{\abs{D}}{L} \expect R_1\cos\fracpart{\lambda + \Phi_1} \\
%&= \big( p + o(1) \big) \expect R_1\cos(\lambda + \Phi_1) \\
%& \hspace{2cm} + \big( d + o(1) \big) \expect R_1\cos\fracpart{\lambda + \Phi_1} \\
&=  p \expect R_1\cos(\lambda + \Phi_1) + d\expect R_1\cos\fracpart{\lambda + \Phi_1} + o(1),
\end{align*}
because $\frac{\abs{P}}{L} \rightarrow p$ and $\frac{\abs{D}}{L} \rightarrow d$ as $L\rightarrow\infty$. Put
\begin{align*}
L(\lambda) &= \sqrt{L}\big( T(\lambda) - G(0) \big) = p q_1(\lambda) + d q_2(\lambda) + o(1),
\end{align*}
where
\[
q_1(\lambda) = \expect R_1\big( \cos(\lambda + \Phi_1) - \cos(\Phi_1) \big),
\]
\begin{equation}
q_2(\lambda) = \expect R_1\big( \cos\fracpart{\lambda + \Phi_1} - \cos\fracpart{\Phi_1} \big). \label{eq:q2def}
\end{equation}
We analyse $q_1(\lambda)$ first.  By a Taylor expansion of $\cos(\lambda + \Phi_1)$ about $\lambda = 0$,
\[
\cos(\lambda + \Phi_1) - \cos(\Phi_1) = -\lambda \big( \sin(\Phi_1) + \zeta(\lambda) \big),
\]
where $\zeta$ is a continuous function with $\zeta(0) = 0$. So,
\begin{align*}
q_1(\lambda) &= -\expect R_1\lambda(\sin(\Phi_1) +  \zeta(\lambda)) \\
&= -\lambda \big( \expect R_1\sin(\Phi_1) +  \zeta(\lambda) \expect R_1 \big) \\
&= \lambda \zeta(\lambda) K,
\end{align*}
since $\expect R_1\sin(\Phi_1) = 0$ because $w_1$ has zero mean,  and $K = \expect R_1$ is a finite constant because $\expect\abs{w_1}$ is finite by assumption in Theorem~\ref{thm:consistency}.  So, 
\begin{align*}
\sqrt{L} q_1(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L \zeta(\hat{\lambda}_L) K = o_P(1)
\end{align*}
because $\sqrt{L} \hat{\lambda}_L$ converges in distribution and $\zeta(\hat{\lambda}_L) = o_P(1)$.  Lemma~\ref{} shows that $\sqrt{L} q_2(\hat{\lambda}_L) = o_P(1)$ also.  Thus 
\[
L(\lambda) = p q_1(\lambda) + d q_2(\lambda) + o(1) = o_P(1)
\]
as reuqired.
\end{IEEEproof}
